---
title: "chapter6"
author: "David Chiu"
date: "Tuesday, January 06, 2015"
output: html_document
---

Classifying data with support vector machine
```{r}
library(C50)
data(churn)
str(churnTrain)
churnTrain = churnTrain[,! names(churnTrain) %in% c("state", "area_code", "account_length") ]
set.seed(2)
ind <- sample(2, nrow(churnTrain), replace = TRUE, prob=c(0.7, 0.3))
trainset = churnTrain[ind == 1,]
testset = churnTrain[ind == 2,]
 library(e1071)
 model  = svm(churn~., data = trainset, kernel="radial", cost=1, gamma = 1/ncol(trainset))
 summary(model)
 #install.packages("klaR"")
 library(klaR) 
 getwd()
 model.light  = svmlight(churn~., data = trainset, kernel="radial", cost=1, gamma = 1/ncol(trainset))
```
Choosing the cost of support vector machine
```{r}
 iris.subset = subset(iris, select=c("Sepal.Length", "Sepal.Width", "Species"), Species %in% c("setosa","virginica"))
plot(x=iris.subset$Sepal.Length,y=iris.subset$Sepal.Width, col=iris.subset$Species, pch=19)
 svm.model = svm(Species ~ ., data=iris.subset, kernel='linear', cost=1, scale=FALSE)
 points(iris.subset[svm.model$index,c(1,2)],col="blue",cex=2)
 w = t(svm.model$coefs) %*% svm.model$SV
 b = -svm.model$rho
 abline(a=-b/w[1,2], b=-w[1,1]/w[1,2], col="red", lty=5)
plot(x=iris.subset$Sepal.Length,y=iris.subset$Sepal.Width, col=iris.subset$Species, pch=19)
 svm.model <- svm(Species ~ ., data=iris.subset, type='C-classification', kernel='linear', cost=10000, scale=FALSE)
 points(iris.subset[svm.model$index,c(1,2)],col="blue",cex=2)
 w <- t(svm.model$coefs) %*% svm.model$SV
 b <- -svm.model$rho
 abline(a=-b/w[1,2], b=-w[1,1]/w[1,2], col="red", lty=5)
```
Visualizing svm fit
```{r}
 data(iris)
 model.iris  = svm(Species~., iris)
 plot(model.iris, iris, Petal.Width ~ Petal.Length, slice = list(Sepal.Width = 3, Sepal.Length = 4))
 plot(model, trainset, total_day_minutes ~ total_intl_charge)
 #?svm.plot  
```
Predicting labels based upon a model  trained by support vector machine
```{r}
 svm.pred <- predict(model, testset[, !names(testset) %in% c("churn")])
 svm.table=table(svm.pred, testset$churn)
 svm.table
 classAgreement(svm.table)
 library(caret)
 confusionMatrix(svm.table)
library(car)
data (Quartet)
 model.regression = svm(Quartet$y1~Quartet$x,type="eps-regression")
 predict.y <- predict(model.regression, Quartet$x) 
 predict.y
 plot(Quartet$x, Quartet$y1, pch=19)
 points(Quartet$x, predict.y, pch=15, col="red")
```
Tuning support vector machine
```{r}
library(e1071)
library(C50)
data(churn)
str(churnTrain)
churnTrain = churnTrain[,! names(churnTrain) %in% c("state", "area_code", "account_length") ]
set.seed(2)
ind <- sample(2, nrow(churnTrain), replace = TRUE, prob=c(0.7, 0.3))
trainset = churnTrain[ind == 1,]
testset = churnTrain[ind == 2,]
#tuned <- tune.svm(churn~., data = trainset, gamma = 10^(-6:-1), cost = 10^(1:2))
 #summary(tuned)
 model.tuned <- svm(churn~., data = trainset, gamma = 10^-2, cost = 100)
 summary(model.tuned)
 svm.tuned.pred <- predict(model.tuned, testset[, !names(testset) %in% c("churn")])
 svm.tuned.table=table(svm.tuned.pred, testset$churn)
 svm.tuned.table
 classAgreement(svm.tuned.table)
 confusionMatrix(svm.tuned.table)
 #?svm.tune
```
Training neural network with neuralnet
```{r}
 data(iris)
 ind <- sample(2, nrow(iris), replace = TRUE, prob=c(0.7, 0.3))
 trainset = iris[ind == 1,]
 testset = iris[ind == 2,]

 #install.packages("neuralnet")
 library(neuralnet)
 trainset$setosa = trainset$Species == "setosa"
 trainset$virginica = trainset$Species == "virginica"
 trainset$versicolor = trainset$Species == "versicolor"
 network = neuralnet(versicolor + virginica + setosa~ Sepal.Length + Sepal.Width + Petal.Length + Petal.Width, trainset, hidden=3)
 network
 network$result.matrix
 head(network$generalized.weights[[1]])
```
Visualizing neural network trained by neuralnet
```{r}
 plot(network)
 par(mfrow=c(2,2))
 gwplot(network,selected.covariate="Petal.Width")
 gwplot(network,selected.covariate="Sepal.Width")
 gwplot(network,selected.covariate="Petal.Length")
 gwplot(network,selected.covariate="Petal.Width")
#?gwplot
```
Predicting labels based upon a model trained by neuralnet
```{r}
 predict = compute(network, testset[-5])$net.result
 prediction = c("versicolor", "virginica", "setosa")[apply(predict, 1, which.max)]
 predict.table = table(testset$Species, prediction)
 predict.table
 classAgreement(predict.table)
 confusionMatrix(predict.table)
 compute(network, testset[-5])
```
Training neural network with nnet
```{r}
library(nnet)
 iris.nn <- nnet(Species ~ ., data = trainset, size = 2, rang = 0.1, decay = 5e-4, maxit = 200)
 summary(iris.nn)
```
Predicting labels based upon a model trained by nnet
```{r}
library(nnet)
 data(iris)
 ind <- sample(2, nrow(iris), replace = TRUE, prob=c(0.7, 0.3))
 trainset = iris[ind == 1,]
 testset = iris[ind == 2,]
iris.nn <- nnet(Species ~ ., data = trainset, size = 2, rang = 0.1, decay = 5e-4, maxit = 200)
 iris.predict = predict(iris.nn, testset, type="class")
 nn.table = table(testset$Species, iris.predict)
 nn.table
 confusionMatrix(nn.table)
 head(predict(iris.nn, testset))
```

