---
title: "chapter4"
author: "David Chiu"
date: "Monday, January 12, 2015"
output: html_document
---

Simple Linear Regression with lm

```{r}
# install.packages("car")
library(car)
data(Quartet)
str(Quartet)
plot(Quartet$x, Quartet$y1)
lmfit = lm(Quartet$y1~Quartet$x)
abline(lmfit, col="red")   
lmfit


plot(Quartet$x, Quartet$y1)
lmfit2 = lsfit(Quartet$x,Quartet$y1)
abline(lmfit2, col="red")  


```

Summarizing Linear Model Fits

```{r}
summary(lmfit)
#?summary.lm
coefficients(lmfit)
confint(lmfit, level=0.95) 
fitted(lmfit) 
residuals(lmfit) 
anova(lmfit) 
vcov(lmfit) 
influence(lmfit)

```
Using Linear Regression to Predict Unknown Values

```{r}
plot(Quartet$x, Quartet$y2)
lmfit = lm(Quartet$y2~ I(Quartet$x)+I(Quartet$x^2))
lmfit = lm(Quartet$y2~poly(Quartet$x,2))
lines(sort(Quartet$x), lmfit$fit[order(Quartet$x)], col = "red")
plot(Quartet$x, Quartet$y2)
lmfit = lm(Quartet$y2~ I(Quartet$x)+I(Quartet$x^2))
```

Robust Linear Regression With rlm 

```{r}
library(MASS)
plot(Quartet$x, Quartet$y3)
lmfit = rlm(Quartet$y3~Quartet$x)
abline(lmfit, col="red")
plot(Quartet$x, Quartet$y3)
lmfit = lm(Quartet$y3~Quartet$x)
abline(lmfit, col="red")
```

A Case Study of Linear Regression On SLID Data

```{r}
library(car)
data(SLID)
str(SLID)
attach(SLID)
par(mfrow=c(2,2))
plot(wages ~ language)
plot(wages ~ age)
plot(wages ~ education)
plot(wages ~ sex)
lmfit <- lm(wages ~ ., data = SLID)
summary(lmfit)
lmfit = lm(wages ~ age + sex + education, data = SLID)
summary(lmfit)
par(mfrow=c(2,2))
plot(lmfit)
par(mfrow=c(2,2))
plot(lmfit)
#?SLID
```

Gaussian Model For Generalized Linear Regression
```{r}
lmfit1 = glm(wages ~ age + sex + education, data = SLID, family=gaussian)
summary(lmfit1)
lmfit2 = lm(wages ~ age + sex + education, data = SLID)
summary(lmfit2)
anova(lmfit1, lmfit2)
```

Poisson Model For Generalized Linear Regression 

```{r}
data(warpbreaks)
head(warpbreaks)
rs1 = glm(breaks ~ tension, data=warpbreaks, family="poisson")
summary(rs1)
```
Binomial Model For Generalized Linear Regression 
```{r}
data(mtcars)
head(mtcars$vs)
lm1 = glm(vs ~ hp+mpg+gear,data=mtcars, family=binomial)
summary(lm1)
lm1 = glm(vs ~ hp+mpg+gear,data=mtcars, family=binomial(link="probit"))
#?family
```
Fit Generalized Addictive Model to Data
```{r}
#install.packages("mgcv")
library(mgcv)

#install.package("MASS")
library(MASS)
attach(Boston)
str(Boston)

fit <- gam(dis ~ s(nox))
summary(fit)
#? bam

```
Visualize Generalized Addictive Model
```{r}
plot(nox, dis)
x <- seq(0, 1, length = 500)
y <- predict(fit, data.frame(nox = x))
lines(x, y, col = "red", lwd = 2)
plot(fit)
fit2=gam(medv~crim+zn+crim:zn, data=Boston)
vis.gam(fit2)
```

Diagnostic of Generalized Addictive Model 

```{r}
gam.check(fit)
#?gam.check
#?choose.k
```