---
title: "Chapter5"
author: "David Chiu"
date: "Tuesday, January 06, 2015"
output: html_document
---
```
install.packages("C50")
```
```{r}
library(C50)
data(churn)
str(churnTrain)
churnTrain = churnTrain[,! names(churnTrain) %in% c("state", "area_code", "account_length") ]
set.seed(2)
ind <- sample(2, nrow(churnTrain), replace = TRUE, prob=c(0.7, 0.3))
trainset = churnTrain[ind == 1,]
testset = churnTrain[ind == 2,]
dim(trainset)
dim(testset)
split.data = function(data, p = 0.7, s = 666){
    set.seed(s)
    index = sample(1:dim(data)[1])
    train = data[index[1:floor(dim(data)[1] * p)], ]
    test = data[index[((ceiling(dim(data)[1] * p)) + 1):dim(data)[1]], ]
    return(list(train = train, test = test))
} 
```
```{r}
library(rpart)
churn.rp <- rpart(churn ~ ., data=trainset)
churn.rp 
printcp(churn.rp)
plotcp(churn.rp)
summary(churn.rp)
```
```
?rpart 
?printcp
?summary.rpart
```{r}
plot(churn.rp, margin= 0.1)
text(churn.rp, all=TRUE, use.n = TRUE)
plot(churn.rp, uniform=TRUE, branch=0.6, margin=0.1)
text(churn.rp, all=TRUE, use.n = TRUE)
predictions <- predict(churn.rp, testset, type="class")
table(testset$churn, predictions)
```
```{r}
library(caret)
confusionMatrix(table(predictions, testset$churn))
min(churn.rp$cptable[,"xerror"])
which.min(churn.rp$cptable[,"xerror"])
churn.cp = churn.rp$cptable[7,"CP"]
churn.cp

prune.tree <- prune(churn.rp, cp= churn.cp)
plot(prune.tree, margin= 0.1)
text(prune.tree, all=TRUE , use.n=TRUE)
predictions <- predict(prune.tree, testset, type="class")
table(testset$churn, predictions)
confusionMatrix(table(predictions, testset$churn))

library(party)
ctree.model <- ctree(churn ~ . , data = trainset)
ctree.model
#help("BinaryTree-class")
plot(ctree.model)
daycharge.model <- ctree(churn ~ total_day_charge, data = trainset)
plot(daycharge.model)

#?plot.BinaryTree
ctree.predict = predict(ctree.model ,testset)
table(ctree.predict, testset$churn)
confusionMatrix(table(ctree.predict, testset$churn))
tr <- treeresponse(ctree.model, newdata = testset[1:5,])
tr

#install.packages("class")
library(class)
levels(trainset$international_plan) = list("0"="no", "1"="yes")
levels(trainset$voice_mail_plan) = list("0"="no", "1"="yes")
levels(testset$international_plan) = list("0"="no", "1"="yes")
levels(testset$voice_mail_plan) = list("0"="no", "1"="yes")
churn.knn  = knn(trainset[,! names(trainset) %in% c("churn")], testset[,! names(testset) %in% c("churn")], trainset$churn, k=3)
summary(churn.knn)
table(testset$churn, churn.knn)
confusionMatrix(table(testset$churn, churn.knn))
fit <- glm(churn ~ ., data = trainset, family=binomial)
summary(fit)
pred = predict(fit,testset, type="response")
Class = pred >.5
summary(Class)
tb = table(testset$churn,Class)
tb
churn.mod = ifelse(testset$churn == "yes", 1, 0)
pred_class = churn.mod
pred_class[pred<=.5] = 1- pred_class[pred<=.5]
ctb = table(churn.mod, pred_class)
ctb
confusionMatrix(ctb)
library(e1071) 
classifier<-naiveBayes(trainset[, !names(trainset) %in% c("churn")], trainset$churn)
classifier
bayes.table = table(predict(classifier, testset[, !names(testset) %in% c("churn")]), testset$churn)
bayes.table
confusionMatrix(bayes.table)
```
